---
title: "Data Recoding"
author: ''
date: '2022-02-23'
slug: data-recoding
categories: []
tags: []
---
**readr**
* read_csv() - comma delimited files
* read_csv2() - semicolon separated files (common in countries where , is used as the decimal place)
* read_tsv() - tab delimited files
* read_delim() - reads in files with any delimiter
* read_fwf() - fixed width files

**readxl**
* read_excel() - read xls or xlsx files

# Reading Data
```{r}
library(tidyverse)
nobel <- read_csv('https://raw.githubusercontent.com/AF11703/tidyverse/main/nobel.csv')
nobel
```
# Writing Data
* Write a file
```{r}
df <- tribble(
  ~x, ~y, 
  1,  "a",
  2,  "b",
  3,  "c",
)
write_csv(df, file = "df.csv")
```
* Read it back in to inspect
```{r}
read_csv("df.csv")
```
# Variable Names
## Data with Bad Names
```{r}
edibnb_badnames <- read_csv("https://raw.githubusercontent.com/AF11703/tidyverse/main/edibnb-badnames.csv")
names(edibnb_badnames)
```
# Variable Types
* Which type is x?
```{r}
dfna.csv <- 'https://raw.githubusercontent.com/AF11703/tidyverse/main/df-na.csv'
  dfna.csv <- read_csv('https://raw.githubusercontent.com/AF11703/tidyverse/main/df-na.csv')
```
## Option 1: Explicit NAs
```{r}
read_csv('https://raw.githubusercontent.com/AF11703/tidyverse/main/df-na.csv',na = c("", "NA", ".", "9999", "Not applicable"))
```
## Option 2: Specify Column Types
```{r}
read_csv("https://raw.githubusercontent.com/AF11703/tidyverse/main/df-na.csv", col_types = list(col_double(), 
                                            col_character(), 
                                            col_character()))
```
# Favorite Foods
```{r}
library(readxl)
fav_food <- read_excel('favourite-food.xlsx', na = c("N/A", "99999")) %>%
janitor::clean_names()

fav_food
```
```{r}
fav_food <- fav_food %>%
  mutate(
    age = if_else(age == "five", "5", age),
    age = as.numeric(age)
  )
glimpse(fav_food)
```
```{r}
fav_food %>%
  count(ses)
```
```{r}
fav_food <- fav_food %>%
  mutate(ses = fct_relevel(ses, "Low", "Middle", "High"))

fav_food %>%
  count(ses)
```
```{r}
fav_food <- read_excel("favourite-food.xlsx", na = c("N/A", "99999")) %>%
  janitor::clean_names() %>%
  mutate(
    age = if_else(age == "five", "5", age), 
    age = as.numeric(age),
    ses = fct_relevel(ses, "Low", "Middle", "High")
  )
fav_food
```
```{r}
fav_food_clean <- read_csv('https://raw.githubusercontent.com/AF11703/tidyverse/main/fav-food-clean.csv')
```
# Other types of Data

* **googlesheets4**: Google Sheets
* **haven**: SPSS, Stata, and SAS files
* **DBI**, along with a database specific backend (e.g. RMySQL, RSQLite, RPostgreSQL etc): allows you to run SQL queries against a database and return a data frame
* **jsonline**: JSON
* **xml2**: xml
* **rvest**: web scraping
* **httr**: web APIs
* **sparklyr**: data loaded into spark
