---
title: "Data Types"
author: ''
date: '2022-02-21'
slug: data-types
categories: []
tags: []
---
```{r}
library(tidyverse)
catlovers <- 'https://raw.githubusercontent.com/AF11703/tidyverse/main/cat-lovers.csv'
cat_lovers <- read_csv(catlovers)
```
### Summarize Cat Lovers Data Set
```{r}
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats, na.rm = TRUE))
```
```{r}
View(cat_lovers)
```

### Fixing bad data
```{r}
cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    ) %>%
  summarise(mean_cats = mean(number_of_cats))
```
```{r}
cat_lovers <- cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    )
```

# Data Types

### Logical = boolean values TRUE and FALSE
```{r}
typeof(TRUE)
```
### Character = character strings
```{r}
typeof("hello")
```
### Double = floating point numerical values (default numerical type)
```{r}
typeof(1.335)
typeof(7)
```
### Integer = integer numerical values (indicated with an L)
```{r}
typeof(7L)
typeof(1:3)
```
### Concatenation - vectors can be constructed using "c()"
```{r}
c(1, 2, 3)
c("Hello", "World!")
c(c("hi", "hello"), c("bye", "jello"))
```
### Converting between types with intention...
```{r}
x <- c(TRUE, FALSE)
x
typeof(x)

y <- as.numeric(x)
y
typeof(y)
```
### Converting between types without intention...
```{r}
c(1, "Hello")
c(FALSE, 3L)
c(1.2, 3L)
c(2L, "two")
```
## Explicit vs. Implicit Coercion
* **Explicit Coercion** is when you call a function like "as.logical()," "as.numeric()," "as.integer()," "as.double()," or "as.character()."

* **Implicit Coercion** happens when you use a vector in a specific context that expects a certain type of vector.

## Special Values
*NA*: Not Available
*NaN*: Not a number
*Inf*: Positive Infinity
*-Inf*: Negative Infinity

```{r}
pi / 0

0 / 0

1/0 - 1/0

1/0 + 1/0
```
```{r}
x <- c(1, 2, 3, 4, NA)
mean(x)
mean(x, na.rm = TRUE)
summary(x)

typeof(NA)
```
### Mental Model for NA's
Why do the following give different answers?
```{r}
# True or NA
TRUE | NA
```
```{r}
# False or NA
FALSE | NA 
```
* NA is unknown, so it could be TRUE or FALSE
```{r}
# TRUE | NA, if NA was TRUE
TRUE | TRUE
```
```{r}
# TRUE | FALSE, if NA was FALSE
TRUE | FALSE
```
```{r}
# FALSE | TRUE, if NA was TRUE
FALSE | TRUE
```
```{r}
# FALSE | FALSE, if NA was FALSE
FALSE | FALSE
```
* Doesn't make sense for mathematical operations
* Makes sense in the context of missing data


