---
title: "Data Classes"
author: ''
date: '2022-02-23'
slug: data-classes
categories: []
tags: []
---
# Factors
* R uses factors to handle categorical variables, variables that have a fixed and known set of possible values.
```{r}
x <- factor(c("BS", "MS", "PhD", "MS"))
x

typeof(x)
class(x)
```
* We can think of factors like character (level labels) and an integer (level numbers) glued together
```{r}
library(tidyverse)
glimpse(x)
as.integer(x)
```
# Dates
```{r}
y <- as.Date("2020-01-01")
y
typeof(y)
class(y)
```
* We can think of dates like an integer (the number of days since the origin, 1 Jan 1970) and an integer (the origin) glued together.
```{r}
as.integer(y)
```
```{r}
as.integer(y) / 365 #Roughly 50 yrs
```
# Data Frames
* We can think of data frames like vectors of equal length glued together.
```{r}
df <- data.frame(x = 1:2, y = 3:4)
df

typeof(df)
class(df)
```
# Lists 
* Lists are a generic vector container, vectors of any type can go in them.
```{r}
l <- list(
  x = 1:4,
  y = c("hi", "hello", "jello"),
  z = c(TRUE, FALSE)
)
l
```
## Lists and Data Frames
* A data frame is a special list containing vectors of equal length.
* When we use the "pull()" fucntion, we extract the vector from the data frame.
```{r}
df
```
```{r}
df %>%
  pull(y)
```
# Working with Factors

## Read Data as Character Strings,
```{r}
catlovers <- 'https://raw.githubusercontent.com/AF11703/tidyverse/main/cat-lovers.csv'
cat_lovers <- read_csv(catlovers)
glimpse(cat_lovers)
```
### But Coerce when Plotting
```{r}
ggplot(cat_lovers, aes(x = handedness)) +
  geom_bar()
```

#### Use Forcats to Manipulate Factors
```{r}
cat_lovers %>%
  mutate(handedness = fct_infreq(handedness)) %>%
  ggplot(aes(x = handedness)) +
  geom_bar()
```
# Make a Date
* **lubridate** is the tidyverse-friendly package that makes dealing with dates a little easier
 
* It's not one of the core tidyverse packages, hence it's installed with *install.packages("tidyverse)* but it's not loaded with it, and needs to be explicitly loaded with *library(lubridate)*

```{r}
hotels <- read_csv('https://raw.githubusercontent.com/AF11703/tidyverse/main/hotels.csv')
hotels %>%
  select(starts_with("arrival_"))
```
## Step 1: Construct Dates
```{r}
library(glue)

hotels %>%
  mutate(
    arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")
  ) %>%
  relocate(arrival_date)
```
## Step 2: Count Bookings per Date
```{r}
hotels %>%
  mutate(arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")) %>%
  count(arrival_date)
```
## Step 3: Visualise Bookings per Date
```{r}
hotels %>%
  mutate(arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")) %>%
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```
### Step 1 (REVISED): Construct Dates "as Dates"
```{r}
library(lubridate)
library(glue)
hotels %>%
  mutate(
    arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))
    ) %>% 
  relocate(arrival_date)
```
### Step 2: Count Bookings per Date 
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date)
```
### Step 3a: Visualise Bookings per Date
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()

```
### Step 3b: Visualise Using a Smooth Curve
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_smooth()
```


