---
title: 'A03: Classification Models'
author: ''
date: '2022-04-01'
slug: a03-classification-models
categories: []
tags: []
---
# Call libraries
```{r}
library(openintro)
library(tidyverse)
library(tidymodels)
library(ggridges)
```

# Import Datasets
```{r}
url1 <- 'https://raw.githubusercontent.com/AF11703/website_delete/main/gender_submission.csv'
gendersubs <- read_csv(url1)

url2 <- 'https://raw.githubusercontent.com/AF11703/website_delete/main/train.csv'
train <- read_csv(url2)

url3 <- 'https://raw.githubusercontent.com/AF11703/website_delete/main/test.csv'
test <- read_csv(url3)
```
```{r}
View(gendersubs)
View(train)
View(test)
```

```{r}
glimpse(train)
```

```{r}
train %>%
  ggplot(aes(x = Pclass, y = Survived, color = Survived)) +
  geom_jitter() +
  labs(
    x = "Passenger Class (from 1-3)",
    y = "Survived",
    title = "Titanic Passengers that Survived and Died"
  ) 
```
In this plot we can see that most of the passengers who passed away were in third class, the lowest socioeconomic standing of the three, while most of the passengers who survived were in first class, the highest socioeconomic standing of the three.


```{r}
train %>%
  group_by(Survived) %>%
  summarise(mean_class = mean(Pclass))
```
 This confirms what we saw in the plot. Therefore, we can make an inference that class is a good indicator for predicting whether a passenger will survive or not.

# Fitting Logistic Regression 
```{r}
d <- tibble(p = seq(0.001, 0.999, length.out = 10000)) %>%
  mutate(logit_p = log(p/(1-p)))

d %>%
  ggplot(aes(x = p, y = logit_p)) +
  geom_line() +
  xlim(0,1) +
  ylab("logit(p)") +
  labs(title = "logit(p) vs. p")
```

```{r}
train$Survived = as.factor(train$Survived)
```


```{r}
survive_fit <- logistic_reg() %>%
  set_engine("glm") %>%
  fit(Survived~Pclass, data = train)
tidy(survive_fit)
```
```{r}
newdata <- tibble(
  Pclass = c(1, 2, 3),
  color = c("#A7D5E8", "#e9d968", "8fada7"),
  shape = c(22, 23, 24)
)

y_hat <- predict(survive_fit, newdata, type = "raw")

p_hat <- exp(y_hat) / (1 + exp(y_hat))

newdata <- newdata %>%
  bind_cols(
    y_hat = y_hat,
    p_hat = p_hat
  )

survive_aug <- augment(survive_fit$fit) %>%
  mutate(prob = exp(.fitted) / (1 + exp(.fitted)))
```
```{r}
ggplot(survive_aug, aes(x = Pclass)) +
  geom_point(aes(y = as.numeric(Survived)-1, color = Survived), alpha = 0.3) +
  scale_color_manual(values = c("#DEB4A0", "#CA235F"))+
  scale_y_continuous(breaks = c(0,1)) +
  guides(color = "none") +
  geom_line(aes(y = prob)) +
  geom_point(data = newdata, aes(x = Pclass, y = p_hat), fill = newdata$color, shape = newdata$shape, stroke = 1, size = 6) +
  labs(
    x = "Class of Passengers",
    y = "Survived",
    title = "Passengers who Survived and Died"
  )
```
 This model suggests that class 3 passengers are more likely to die on the Titanic, whereas class 2 and 1 passengers are more likely to survive, with class 1 passengers being the most likely. With this in mind, it is not out of the question to look at the passengers within the "test" data set and give passengers within class 3 a low chance of surviving while giving passengers within class 1 a high chance of surviving. 
