---
title: "R markdown practice"
author: ''
date: '2022-02-16'
slug: r-markdown-practice
categories: []
tags: []
---

```{r, warning = FALSE, message = FALSE, results = FALSE}
library(datasets)
data(iris)
#Load packages
pkgs <- c("rstatix", "emmeans", "psych", "tidyr", "tidyverse", "psych", "dplyr", "ggplot2", "lm.beta", "car", "Hmisc", "skimr", "janitor")
lapply(pkgs, library, character.only = TRUE)
```

# Intro


## Code Chunks
```{r}
summary(iris)
```
```{r}
#Sum of 2 + 2
2 + 2

#Average Sepal Length
mean(iris$Sepal.Length)
```
```{r}
#Levels of Species
unique(iris$Species)
```
#Text
*italics* and _italics_
**bold** and __bold__
superscript^2^
~~strikethrough~~
[link](www.rstudio.com)

#Headers
```{r}
# Header 1
## Header 2
```
### Header 3
#### Header 4
##### Header 5
###### Header 6

## Symbols
endash: --
emdash: ---
ellipsis: ...
incline equation: $A = \pi*r^{2}$

horizontal rule 

***

> block quote

* unordered list
* item 2
  + sub-item 1
  + sub-item 2
  
1. ordered list
2. item 2
  + sub-item 1
  + sub-item 2

First Header | Second Header 
-------------|--------------
Table Cell 1 |Cell 2
Cell 3 | Cell 4

## Date
```{r, eval = FALSE}
Sys.Date()
```
# Code Specifications

## Display Code
```{r, echo = FALSE, eval = FALSE}
echo = TRUE: Whether to display code along with results
Default is echo = TRUE
```

```{r, echo = FALSE}
summary(iris)
```

## Display warnings
```{r, warning = FALSE, eval = FALSE}
warning = TRUE: Whether to display warnings
```
### With warning
```{r, warning = TRUE}
data <- data.frame(x = 1 : 5,    # Create example data
                   y= 1 : 5)

ggp <- ggplot(data, aes(x, y)) + # Create ggplot2 w/ default...
  geom_point()

ggp +                            # Modify axis limits
  scale_x_continuous(limits = c(2,5))
```
## Without warning
```{r, warning = FALSE}
data <- data.frame(x = 1 : 5,    # Create example data
                   y= 1 : 5)

ggp <- ggplot(data, aes(x, y)) + # Create ggplot2 w/ default...
  geom_point()

ggp +                            # Modify axis limits
  scale_x_continuous(limits = c(2,5))
```
## Display Output, Output included 
```{r, results = TRUE}
summary(iris)
```
## Output not Included
```{r, results = FALSE}
summary(iris)
```
## Display Messages
Default message = TRUE

## Messages not Included
```{r, message = FALSE, results = FALSE}
# load packages
pkgs <- c("rstatix", "emmeans", "psych", "tidyr", "tidyverse", "psych", "dplyr", "ggplot2", "lm.beta", "car", "Hmisc", "skimr", "janitor")
lapply(pkgs, library, character.only = TRUE)
```
## Bold Code
```{r}
### <b>
x  <- 10
y <- x * 2
### <b>
```

# Advanced Inline Code
```{r}
# Run ANOVA
model <- aov(Sepal.Length ~ Species, data = iris)
summary(model)

# Create clean tibble from output using broom package
library(broom)
modelmatrix <- broom::tidy(model)

# Round to 3 decimals for clean output
modelmatrix$statistic <- sprintf(modelmatrix$statistic, fmt = '%#.3f')
modelmatrix$p.value <- sprintf(modelmatrix$p.value, fmt = '%#.3f')

modelmatrix
```

